\bf\mftitle

### 2011-01-25 doc/jInfer/basicdtd/basicdtd.tex
Documentation.

>>>>

\subsection{Preferences}

All settings provided by \jmodule{BasicDTDExporter} are project-wide, the preferences panel is in \code{cz.cuni.mff.ksi.jinfer.basicdtd.properties} package. As mentioned before, it is possible to set the following. 
\begin{itemize}
	\item Maximum attribute domain size which is exported as a list of all values (\code{(a|b|c)} notation).
	\item Minimal ratio an attribute value in the domain needs to have in order to be declared default.
\end{itemize}

### 2011-01-25 doc/jInfer/basicigg/basicigg.tex
Documentation: BasicIGG - process view schema.
Documentation.

The main class implementing \code{IGGenerator} inference interface and simultaneously registered as its service provider is \code{IGGeneratorImpl}. In its \code{start} method it enumerates all files in the input parameter (of type \code{Input}). For each file, based on its extension the correct \emph{processor} is selected, executed and returned rules are aggregated. After each file has been processed, the resulting grammar is returned by invoking the \code{finished} method of the callback argument.

@@

>>>>

The main class implementing \code{IGGenerator} inference interface and simultaneously registered as its service provider is \code{IGGeneratorImpl}. In its \code{start} method it enumerates all files in the input parameter (of type \code{Input}). For each file, based on its extension the correct \emph{processor} is selected, executed and returned rules are aggregated. After each file has been processed, the resulting grammar is returned by invoking the \code{finished} method of the callback argument. This process is illustrated in fig. \ref{figure-process}.

\begin{figure}
	\centering\includegraphics[scale=\myscale]{process-view}
	\caption{Process view of BasicIGG} \label{figure-process}
\end{figure}

@@

\section{Preferences}

All settings provided by \jmodule{BasicIGG} are project-wide, the preferences panel is in \code{cz.cuni.mff.ksi.jinfer.basicigg.properties} package. It is possible to set the following flags. 
\begin{itemize}
	\item Flag to keep values of attributes found in XML documents - unchecking this saves memory during the inference process, but loses all information about the attribute domain, which can lead to less expressive schema.
	\item Flag to keep simple data values from XML documents - again, unchecking saves memory (potentially a lot, with input files containing a lot of text). Drawback might again be losing information that could be useful in schema generation.
	\item Flag to stop on errors: if this flag is set, \jmodule{BasicIGG} will interrupt the inference if it comes across an error while extracting IG. Unsetting this flag allows \jmodule{BasicIGG} to ignore these errors and retrieve as much IG as possible.
\end{itemize}
